---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ohno

<!-- badges: start -->
<!-- badges: end -->

The goal of ohno is to check a potential workaround when an existing package (in this case ohno) defines a functional (`ohno::butcher`) that modifies the environment associated with the user-supplied function, with the result that the created closures can be bizarre.

```{r eval=FALSE}
remotes::install_github("djnavarro/ohno")
```

Here's the problem:

```{r example, error=TRUE}
library(ohno)

add_with <- function(z) {
  function(x,y) {x + y + z}
}

# ideally we want these to both return 7...
operate(x = 2, y = 4, add_with(z = 1))
butcher(x = 2, y = 4, add_with(z = 1))
```

What's going on here is that the `operate()` function does exactly what you'd expect:

```{r}
operate
```

whereas `butcher()` does something weird, and breaks the `adds_with()` closure:

```{r}
butcher
```

A simple fix that doesn't require the user to inject values into the hidden `env` environment is to use `substitute()` to evaluate `z` early:

```{r}
add_with <- function(z) {
  eval(substitute(function(x,y){x + y + z}))
}

operate(2, 4, add_with(1))
butcher(2, 4, add_with(1))
```
